Evaluating Class Imbalance

### 2019-05-14 Scripts/calculating_jaccard_index_between_annotations.Rmd
editted results scripts

>>>>

```{r}
jaccard.mat.k562 <- readRDS("Z:/TAD_data_analysis/jaccard/jaccard.mat.k562.rds")
jaccard.mat.k562 <- jaccard.mat.k562[!duplicated(rownames(jaccard.mat.k562)), !duplicated(colnames(jaccard.mat.k562))]

```{r}
css <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
css <- css[grep("K562", css)]
css <- gsub(paste(c("K562-", ".bed"), collapse = "|"), "", css)
jaccard.mat.k562.css <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% css, colnames(jaccard.mat.k562) %in% css]

corrplot(jaccard.mat.k562.css, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

upper_tri_css <- get_upper_tri(jaccard.mat.k562.css)
melted_css <- reshape2::melt(upper_tri_css, na.rm = TRUE)
melted_css <- melted_css[-which(melted_css$Var1==melted_css$Var2),]
summary(melted_css$value)
```

```{r}
hm <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
hm <- hm[grep("K562", hm)]
hm <- gsub(paste(c("K562-", ".bed"), collapse = "|"), "", hm)
jaccard.mat.k562.hm <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% hm, colnames(jaccard.mat.k562) %in% hm]

corrplot(jaccard.mat.k562.hm, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

upper_tri_hm <- get_upper_tri(jaccard.mat.k562.hm)
melted_hm <- reshape2::melt(upper_tri_hm, na.rm = TRUE)
melted_hm <- melted_hm[-which(melted_hm$Var1==melted_hm$Var2),]
summary(melted_hm$value)
```

```{r}
tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/k562")
tfbs <- tfbs[grep("K562", tfbs)]
tfbs <- gsub(paste(c("K562-", ".bed","-Haib","-Sydh","-Uta","-Uw","-Broad","-Uchicago"), collapse = "|"), "", tfbs)
jaccard.mat.k562.tfbs <- jaccard.mat.k562[rownames(jaccard.mat.k562) %in% tfbs, colnames(jaccard.mat.k562) %in% tfbs]

corrplot(jaccard.mat.k562.tfbs, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .6,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

upper_tri_tfbs <- get_upper_tri(jaccard.mat.k562.tfbs)
melted_tfbs <- reshape2::melt(upper_tri_tfbs, na.rm = TRUE)
melted_tfbs <- melted_tfbs[-which(melted_tfbs$Var1==melted_tfbs$Var2),]
summary(melted_tfbs$value)
```

```{r}
corrplot(jaccard.mat.k562, method = "square",
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("white", "red"))(100),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

all_melted_k562 <- rbind.data.frame(melted_css,
                                       melted_hm,
                                       melted_tfbs)
all_melted_k562$annotation <- c(rep("CSS", length(melted_css$Var1)),
                                   rep("HM", length(melted_hm$Var1)),
                                   rep("TFBS", length(melted_tfbs$Var1)))
all_melted_k562$annotation <- factor(all_melted_k562$annotation, levels=c("CSS", "HM", "TFBS"))

ggplot(all_melted_k562[-which(all_melted_k562$annotation=="CSS"),], aes(x=value, group=annotation, color=annotation)) + 
  geom_density(size=1) +
  xlim(0,1) +
  xlab("Jaccard Index") +
  ylab("Density") +
  scale_color_discrete(name="Annotation Group") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
     axis.text.y = element_text(size=15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))
```

### 2019-05-14 Scripts/evaluating_imbalance_ratios.Rmd
editted results scripts

#Evaluating Imbalance Ratios
##GM12878
###10kb

@@

# Combined Plots

@@

@@

```{r}
cl.per.chr <- character()
res.per.chr <- character()
chr.per.chr <- character()
bins.per.chr <- numeric()
bounds.per.chr <- numeric()
ir.per.chr <- numeric()

@@

@@

@@

irtab <- cbind.data.frame(cl.per.chr,
                          res.per.chr,
                          chr.per.chr,
                          bins.per.chr,
                          bounds.per.chr,
                          ir.per.chr)
colnames(irtab) <- c("cl","res","chr","bins","bounds","ir")

irtab_summ <- irtab %>%
  group_by(cl, res) %>%
  summarise(AveBins = mean(bins, na.rm = TRUE),
            AveBinsSD = sd(bins, na.rm = TRUE),
            AveBounds = mean(bounds, na.rm = TRUE),
            AveBoundsSD = sd(bounds, na.rm = TRUE),
            AveIR = mean(ir, na.rm = TRUE),
            AveIRSD = sd(ir, na.rm = TRUE))
```

>>>>

#Evaluating Imbalance Ratios

<!--
##GM12878
###10kb

@@

```		
-->

<!--	
# Combined Plots

@@

```
-->

@@

```{r}
cl.per.chr <- character()
res.per.chr <- character()
chr.per.chr <- character()
bins.per.chr <- numeric()
bounds.per.chr <- numeric()
ir.per.chr <- numeric()
tads.per.chr <- numeric()

@@

      tad_dat <- read.table(paste0("Z:/TAD_data_analysis/GSE63525_data/arrowhead_output/",
                                            i,
                                            "/",
                                            paste0(i,"_domain_data_", gsub("kb", "000", j), ".b.txt")))

@@

      tads.per.chr <- rbind(tads.per.chr, dim(tad_dat[which(tad_dat$V1==k),])[1])

@@

irtab <- cbind.data.frame(cl.per.chr,
                          res.per.chr,
                          chr.per.chr,
                          bins.per.chr,
                          tads.per.chr,
                          bounds.per.chr,
                          ir.per.chr)
colnames(irtab) <- c("cl","res","chr","bins","tads","bounds","ir")
irtab$res <- factor(irtab$res, levels=c("10kb","25kb","50kb","100kb"))

irtab_summ <- irtab %>%
  group_by(cl, res) %>%
  dplyr::summarise(AveBins = mean(bins, na.rm = TRUE),
            AveBinsSD = sd(bins, na.rm = TRUE),
            AveTADs = mean(tads, na.rm = TRUE),
            AveTADsSD = sd(tads, na.rm = TRUE),
            AveBounds = mean(bounds, na.rm = TRUE),
            AveBoundsSD = sd(bounds, na.rm = TRUE),
            AveIR = mean(ir, na.rm = TRUE),
            AveIRSD = sd(ir, na.rm = TRUE))
```

# ICC

## GM12878

### Number of genomic bins

```{r}
gbins <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,4)], idvar = "chr", timevar = "res", direction = "wide")
icc(gbins[,-1], model="twoway")
```

### Number of TADs

```{r}
tads <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,5)], idvar = "chr", timevar = "res", direction = "wide")
icc(tads[,-1], model="twoway")
```

### Number of boundaries

```{r}
bounds <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,6)], idvar = "chr", timevar = "res", direction = "wide")
icc(bounds[,-1], model="twoway")
```

### IR

```{r}
imbratio <- reshape(irtab[which(irtab$cl=="GM12878"),c(2,3,7)], idvar = "chr", timevar = "res", direction = "wide")
icc(imbratio[,-1], model="twoway")
```

## K562

### Number of genomic bins

```{r}
gbins <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,4)], idvar = "chr", timevar = "res", direction = "wide")
icc(gbins[,-1], model="twoway")
```

### Number of TADs

```{r}
tads <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,5)], idvar = "chr", timevar = "res", direction = "wide")
icc(tads[,-1], model="twoway")
```

### Number of boundaries

```{r}
bounds <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,6)], idvar = "chr", timevar = "res", direction = "wide")
icc(bounds[,-1], model="twoway")
```

### IR

```{r}
imbratio <- reshape(irtab[which(irtab$cl=="K562"),c(2,3,7)], idvar = "chr", timevar = "res", direction = "wide")
icc(imbratio[,-1], model="twoway")
```
